### 2017-03-02 Lab_4/solutions/L4-2-1.tex
Writing Lab_4 report, finished up to and including WEP. Also limited the large tcpdump file as requested in the assignment.
Former-commit-id: 2a11c5b2f9b9fb43ef3661baec594f748e630830 [formerly d546ff20c73c904d4e0664d4c3f9585b6471a25c [formerly 3ee733a48a147ab31686d313d13ef3aabeb27e5f] [formerly 3ee733a48a147ab31686d313d13ef3aabeb27e5f [formerly 7fc75470399e852cd4643990a68d792c4b53d991]]]
Former-commit-id: 321cb65de5c4cba73812455b6519f7c29ef1b513
Former-commit-id: 9cf2e3208c311f8ec1756e80fe0865e862a1800e
Former-commit-id: 2c06f5e18aa0db19e5d3cf09151c70a741420314

in de eerdere kreeg authentication als reply succesful, nu is het unspecified failure
<pkt ids>

>>>>

In the first dump, when the station sent an authentication frame (pkt ID 2666) it was
followed by an authentication frame (pkt ID 2668) indicating the succesful authentication
of STA with AP in the WLAN management frame status code.\\
In the second case, with mac filtering enabled and configured to not allow STA1's wlan0 to connect,
the authentication frame(pkt ID 464) sent by STA1 is met with an authentication frame(pkt ID 466iperf) sent by the AP
with a status code 0x0001 signalling an unspecified failure which prevents the establishment of STA's connection with AP.

### 2017-03-02 Lab_4/solutions/L4-2-2.tex
Writing Lab_4 report, finished up to and including WEP. Also limited the large tcpdump file as requested in the assignment.
Former-commit-id: 2a11c5b2f9b9fb43ef3661baec594f748e630830 [formerly d546ff20c73c904d4e0664d4c3f9585b6471a25c [formerly 3ee733a48a147ab31686d313d13ef3aabeb27e5f] [formerly 3ee733a48a147ab31686d313d13ef3aabeb27e5f [formerly 7fc75470399e852cd4643990a68d792c4b53d991]]]
Former-commit-id: 321cb65de5c4cba73812455b6519f7c29ef1b513
Former-commit-id: 9cf2e3208c311f8ec1756e80fe0865e862a1800e
Former-commit-id: 2c06f5e18aa0db19e5d3cf09151c70a741420314

Mac address spoof. either two mac addresses will be on the network causing problems and crashing the network or the spoofed mac address will not be present at the time granting the attacker access to the network.

>>>>

This security measure can be circumvented by spoofing our MAC-address to be among those listed in the accepted MAC addresses. \\ \\In the case that the original device
as well as the one we're currently spoofed as are present in the network, problems will arise in the network and things will break (the manner in which they break is
dependent on the type of APs and drivers used.). In the second case, when the original device is no longer present in the network
(this could be ensured by executing a deauthentication attack on the original device), the attacker will be able to access the network using the spoofed MAC address.
